\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}

\title{Evolution of Modern Health Care System}
\author{A056 Shrestha Dupare}
\date{1 February 2022}

\begin{document}

\maketitle

\section{Modern Healthcare}

Modern healthcare has been shaped and transformed by technology. The rise of a consumer culture where people can buy the services they want, has also impacted modern healthcare.


For decades, technology has been used to operate specialist machinery. Other than this, technology has also been increasingly used to provide a better patient experience and run a more efficient and streamlined practice. It has also adopted new ways of working and cooperating with patients alongside providing expected standards of care.


Here are some common features of modern healthcare, which helped in its evolution:

\subsection{Improved doctor-patient communication}

Improving patient satisfaction has been a priority for most of the medical practices in the past few years. The drive towards patient centric care has been the key facet of modern healthcare. Patient interaction has been extended beyond the conventional methods. Following this, a study from the Journal of the American Board of Family Medicine shows that, when email was used for communications between doctor and patients, both of them were more satisfied.And to ensure 


Another way medical practices has implemented modern healthcare system to further improve communication between patient and doctors is by the use of video messaging. Video messaging makes it possible for doctors to consult with their patients, at a time and a place which is comfortable to both parties.


\subsection{Efficient recording of information in real-time}

Modern healthcare is driven by data. Modern healthcare has improved the information recording process. Results, patient information and reports are updated into a system that can be accessed by different healthcare professionals. Additionally mobile devices are used to update conversation between patients and doctor in real-time. This leads to more accurate information recording compared to the conventional method of an assistant keeping manual records, which could lead to errors.


Electronic health record (EHR) systems, like Project Fusion has been introduced in the past few years, which include features such as centralized chart management to enable medical practitioners to access patient records anywhere, anytime and on any device. An EHR system is now considered an important factor in modern healthcare as it ensures communication between other medical professionals like, insurance companies and diagnostic centres, all of them kept in a central place.


\subsection{More collaboration}

There has been a trend involving healthcare companies and the companies outside of healthcare sector forming collaborations to provide better and more comprehensive services to patients. The most recent example is the announcement of the collaboration of Amazon, Berkshire Hathaway, and JPMorgan to form an independent healthcare company.


\subsection{Better connectivity with Internet of Things (IoT)}

The IoT is when physical devices (known as 'smart' devices) are embedded with software, sensors, and electronics to collect and exchange data. The IoT has become an increasing fixture in the modern healthcare. The growth of Iot has contributed to the following:

\begin{itemize}

    \item An increase in the number of wearable devices
    \item Better access to high speed internet
    \item Cheaper treatment and disease management
    
\end{itemize}

There are many applications of IoT in modern healthcare, such as remote monitoring and medical devices integration etc. Companies like Amazon and Google are already utilizing IoT for their Amazon Echo and Google Home voice controlled personal-assistants. These smart speakers have been useful to patient by reminding them to take their medications on time.


\subsection{Rise in Wearable Devices}

According to a recent survey in 2019, it shows that around 30 percent Indians own a smart wearable. These devices are used to track sleep, exercise and heart rates. This aspect of modern healthcare has made the consumers take a more proactive approach to maintaining their health.


Wearable devices has been developed for the specific use of patient care. For example, Philips has introduced a medical grade wearable biomedical sensor which monitors the vitals of an at-risk patient as they move through the hospital.

\end{document}
