\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\title{5 Solutions to Covid 19 provided by Biomedical Engineers}
\author{A056 Shrestha Dupare}
\date{1 March 2022}

\begin{document}

\maketitle

\section{Surgical masks}

Surgical masks have become more common in public places such as malls and metro stations. In reality, some pharmacies claimed that the medicine was unavailable. A surgical mask is a single-use medical device that protects users from infectious pathogens spread by droplets. In the trying times of COVID-19, biomedical engineers helped in making masks and meeting the ever growing demand of it. 


\section{Respirators}

 While surgical masks might not be the most effective way to cover from coronavirus, a further specialised mask, known as an N95 respirator, is said to be more effective. The respirator, a type of personal protection equipment (PPE), is thicker than a surgical mask and have been designed to achieve a veritably close facial fit in order to offer effective filtration of airborne particles. When duly fitted, these can filter further airborne particles than face masks. Amazon users have reportedly looked for the term "N95 mask" over 862,000 times.


\section{Gloves}

Since it is unimaginable to expect to wash hands as much of the time as could be expected, there has been an ascent popular for both sterile and test gloves for infection protection. The gloves should be changed day by day and wearing the right gloves will guarantee that the pollutants won't be consumed and can decrease the possibility contracting infections. As of late, to shield themselves from COVID-19, two travelers loaded up an Australian flight altogether enclosed by full-body plastic sheets with covers, gloves and make-shift full-body plastic suits!


\section{PCR-Kits}

Right now, pandemic-inclined illnesses, for example, Covid, are analyzed by polymerase chain response (PCR), a sub-atomic procedure. Organizations, for example, Primerdesign and Kogene Biotech have delivered PCR packs that can assist with diagnosing the illness. In China, there has been a deficiency in Covid test units, which has postponed analyses, and individuals are saying that getting one is like "scoring the lottery."


\section{Oxygen therapy machines}

A pulse oximeter is a small gadget that uses infrared light refraction to detect how efficiently oxygen binds to your red blood cells. It commonly slides over your fingertip or clips on your ear lobe. The oxygen saturation measurement known as peripheral capillary oxygen saturation, or SpO2, is used by oximeters to report blood oxygen levels. COVID-19 enters the body through the respiratory framework, making direct injury to an individual's lungs by means of irritation and pneumonia - the two of which can contrarily affect how well oxygen is moved into the circulation system. Hence it has been helping in monitoring oxygen levels in home and also sometimes also helping in early detection of COVID.

\end{document}
